Data_visualization

### 2018-08-03 Rmd/Data_visualization.Rmd
last changes

pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="IPPU 50 %"] <- "Ipomoea purpurea"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"

@@

a <- ggplot(pein_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
  labs(title="Petunia integrifolia",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

@@

caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"

#Different colour per family
b <- ggplot(caan_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
  labs(title="Capsicum annuum",x="", y = "")+aes(fill=Family)+theme(axis.text.x = element_blank())+
  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

@@

soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"

#Different colour per family
c <- ggplot(soly_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
  labs(title="Solanum lycopersicum",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

@@

some_seed_set_final$Treatment[some_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
some_seed_set_final$Treatment[some_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
some_seed_set_final$Treatment[some_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
some_seed_set_final$Treatment[some_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
some_seed_set_final$Treatment[some_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
some_seed_set_final$Treatment[some_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
some_seed_set_final$Treatment[some_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
some_seed_set_final$Treatment[some_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
some_seed_set_final$Treatment[some_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
some_seed_set_final$Treatment[some_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"

#Different colour per family
d <- ggplot(some_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
  labs(title="Solanum melongena",x="", y = "")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

@@

brol_seed_set_cross <- filter(brol_seed_set_bind, non_focal %in% c("Cross"))
brol_seed_set_self <- filter(brol_seed_set_bind, non_focal %in% c("Self"))
brol_seed_set_control <- filter(brol_seed_set_bind, non_focal %in% c("Control"))
brol_seed_set_flower <- filter(brol_seed_set_bind, non_focal %in% c("FC"))

@@

# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
brol_seed_set_bind=brol_seed_set_bind[brol_seed_set_bind$non_focal!=c("Cross"),]
brol_seed_set_bind=brol_seed_set_bind[brol_seed_set_bind$non_focal!=c("Self"),]
brol_seed_set_bind=brol_seed_set_bind[brol_seed_set_bind$non_focal!=c("Control"),]
brol_seed_set_bind=brol_seed_set_bind[brol_seed_set_bind$non_focal!=c("FC"),]

@@

brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"

#Different colour per family
a <- ggplot(brol_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
  labs(title="Brassica oleracea",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_blank())+
  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

@@

brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"

#Different colour per family
b <- ggplot(brra_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
  labs(title="Brassica rapa",x="", y = "")+aes(fill=Family)+theme(axis.text.x = element_blank())+
  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

@@

ersa_seed_set_cross <- filter(ersa_seed_set_bind, non_focal %in% c("Cross"))
ersa_seed_set_self <- filter(ersa_seed_set_bind, non_focal %in% c("Self"))
ersa_seed_set_control <- filter(ersa_seed_set_bind, non_focal %in% c("Control"))
ersa_seed_set_flower <- filter(ersa_seed_set_bind, non_focal %in% c("FC"))

@@

# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
ersa_seed_set_bind=ersa_seed_set_bind[ersa_seed_set_bind$non_focal!=c("Cross"),]
ersa_seed_set_bind=ersa_seed_set_bind[ersa_seed_set_bind$non_focal!=c("Self"),]
ersa_seed_set_bind=ersa_seed_set_bind[ersa_seed_set_bind$non_focal!=c("Control"),]
ersa_seed_set_bind=ersa_seed_set_bind[ersa_seed_set_bind$non_focal!=c("FC"),]

@@

ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"

#Different colour per family
c <- ggplot(ersa_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
  labs(title="Eruca versicaria",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
#
##
###
#S. ALBA  
###
##
#

@@

sial_seed_set_cross <- filter(sial_seed_set_bind, non_focal %in% c("Cross"))
sial_seed_set_self <- filter(sial_seed_set_bind, non_focal %in% c("Self"))
sial_seed_set_control <- filter(sial_seed_set_bind, non_focal %in% c("Control"))
sial_seed_set_flower <- filter(sial_seed_set_bind, non_focal %in% c("FC"))

@@

# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
sial_seed_set_bind=sial_seed_set_bind[sial_seed_set_bind$non_focal!=c("Cross"),]
sial_seed_set_bind=sial_seed_set_bind[sial_seed_set_bind$non_focal!=c("Self"),]
sial_seed_set_bind=sial_seed_set_bind[sial_seed_set_bind$non_focal!=c("Control"),]
sial_seed_set_bind=sial_seed_set_bind[sial_seed_set_bind$non_focal!=c("FC"),]

@@

>>>>

pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="IPPU 50 %"] <- "Ipomoea purpurea"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="CROSS"] <- "Cross"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="SELF"] <- "Self"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="CONTROL"] <- "Control"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="FLOWER CONTROL"] <- "Flower control"

@@

a <- ggplot(pein_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Petunia integrifolia",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family)) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

@@

caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="CROSS"] <- "Cross"
caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="SELF"] <- "Self"
caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="CONTROL"] <- "Control"
caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="FLOWER CONTROL"] <- "Flower control"

#Different colour per family
b <- ggplot(caan_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Capsicum annuum",x="", y = "")+aes(fill=Family)+theme(axis.text.x = element_blank())+
  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family)) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

@@

soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="CROSS"] <- "Cross"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="SELF"] <- "Self"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="CONTROL"] <- "Control"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="FLOWER CONTROL"] <- "Flower control"

#Different colour per family
c <- ggplot(soly_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Solanum lycopersicum",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family)) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

@@

some_seed_set_final$Treatment[some_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
some_seed_set_final$Treatment[some_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
some_seed_set_final$Treatment[some_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
some_seed_set_final$Treatment[some_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
some_seed_set_final$Treatment[some_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
some_seed_set_final$Treatment[some_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
some_seed_set_final$Treatment[some_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
some_seed_set_final$Treatment[some_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
some_seed_set_final$Treatment[some_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
some_seed_set_final$Treatment[some_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
some_seed_set_final$Treatment[some_seed_set_final$Treatment=="CROSS"] <- "Cross"
some_seed_set_final$Treatment[some_seed_set_final$Treatment=="SELF"] <- "Self"
some_seed_set_final$Treatment[some_seed_set_final$Treatment=="CONTROL"] <- "Control"
some_seed_set_final$Treatment[some_seed_set_final$Treatment=="FLOWER CONTROL"] <- "Flower control"

#Different colour per family
d <- ggplot(some_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Solanum melongena",x="", y = "")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family)) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

@@

brol_seed_set_cross <- filter(brol_seed_set_bind, non_focal %in% c("Cross"))
brol_seed_set_self <- filter(brol_seed_set_bind, non_focal %in% c("Self"))
brol_seed_set_control <- filter(brol_seed_set_bind, non_focal %in% c("Control"))
brol_seed_set_flower <- filter(brol_seed_set_bind, non_focal %in% c("Flower"))

@@

# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
brol_seed_set_bind=brol_seed_set_bind[brol_seed_set_bind$non_focal!=c("Cross"),]
brol_seed_set_bind=brol_seed_set_bind[brol_seed_set_bind$non_focal!=c("Self"),]
brol_seed_set_bind=brol_seed_set_bind[brol_seed_set_bind$non_focal!=c("Control"),]
brol_seed_set_bind=brol_seed_set_bind[brol_seed_set_bind$non_focal!=c("Flower"),]

@@

brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="FC"] <- "Flower control"

#Different colour per family
a <- ggplot(brol_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Brassica oleracea",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_blank())+
  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family)) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

@@

brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="FC"] <- "Flower control"

#Different colour per family
b <- ggplot(brra_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Brassica rapa",x="", y = "")+aes(fill=Family)+theme(axis.text.x = element_blank())+
  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family)) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

@@

ersa_seed_set_cross <- filter(ersa_seed_set_bind, non_focal %in% c("Cross"))
ersa_seed_set_self <- filter(ersa_seed_set_bind, non_focal %in% c("Self"))
ersa_seed_set_control <- filter(ersa_seed_set_bind, non_focal %in% c("Control"))
ersa_seed_set_flower <- filter(ersa_seed_set_bind, non_focal %in% c("Flower"))

@@

# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
ersa_seed_set_bind=ersa_seed_set_bind[ersa_seed_set_bind$non_focal!=c("Cross"),]
ersa_seed_set_bind=ersa_seed_set_bind[ersa_seed_set_bind$non_focal!=c("Self"),]
ersa_seed_set_bind=ersa_seed_set_bind[ersa_seed_set_bind$non_focal!=c("Control"),]
ersa_seed_set_bind=ersa_seed_set_bind[ersa_seed_set_bind$non_focal!=c("Flower"),]

@@

ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="FC"] <- "Flower control"

#Different colour per family
c <- ggplot(ersa_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Eruca versicaria",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family)) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
#
##
###
#S. ALBA  
###
##
#

@@

sial_seed_set_cross <- filter(sial_seed_set_bind, non_focal %in% c("Cross"))
sial_seed_set_self <- filter(sial_seed_set_bind, non_focal %in% c("Self"))
sial_seed_set_control <- filter(sial_seed_set_bind, non_focal %in% c("Control"))
sial_seed_set_flower <- filter(sial_seed_set_bind, non_focal %in% c("Flower"))

@@

# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
sial_seed_set_bind=sial_seed_set_bind[sial_seed_set_bind$non_focal!=c("Cross"),]
sial_seed_set_bind=sial_seed_set_bind[sial_seed_set_bind$non_focal!=c("Self"),]
sial_seed_set_bind=sial_seed_set_bind[sial_seed_set_bind$non_focal!=c("Control"),]
sial_seed_set_bind=sial_seed_set_bind[sial_seed_set_bind$non_focal!=c("Flower"),]

@@

```
```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3.7, fig.width=7,out.width='100%'}

library(reshape2)
library(ggplot2)
library(dplyr)
library(gridExtra)
library(grid)
library(lattice)

#Preparing seed set plots, starting with Petunia
#
##
###
#I. AQUATICA
###
##
#

ipaq_seed_set <- read.csv("Data/ipaq_seed_set.csv", sep=";")
colnames(ipaq_seed_set)[1] <- "Species"
colnames(ipaq_seed_set)[2] <- "Treatment"
colnames(ipaq_seed_set)[3] <- "Treatment.number"
colnames(ipaq_seed_set)[4] <- "Seed.production"

ipaq_seed_set <- filter(ipaq_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%"& Treatment!="COSA 50%"& Treatment!="COSA 100%" )

#adding the focal species, first 50%
Species <- rep("IPAQ", 10)
Treatment <- rep("IPAQ 50%", 10)
Treatment.number <- seq(1:10)
Seed.production <- rep(0, 10)
ipaq_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
#adding the focal species, 100%
Species <- rep("IPAQ", 10)
Treatment <- rep("IPAQ 100%", 10)
Treatment.number <- seq(1:10)
Seed.production <- rep(0, 10)
ipaq_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
#Order from lower to higher values the average, to plot it nicely
